---
title: "Lab4_Vignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Lab4_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(Math4753GKDeasonLab4S3)
```


# The Package

This package contains 3 functions. 

  1. mybiplot
  
   _mybiplot_ serves as an S3 constructor. It has 2 arguments (x = double, k = double) where x is a vector of continuous quantitative values and k is a vector constant. It takes the vector passed to x and transforms it into a categorical variable named "inout". When x is within k standard deviations of the mean of x, inout returns "in". When x is greater than k standard deviations of the mean of x, inout returns "outu". Otherwise inout returns "outl". Additionally, _mybiplot_ assigns the class "math4753GbiplotKDeason" to the new object.
    _Examples:_
```{r}
mpg <- epa$MPG
unclass(mybiplot(x = mpg[1:5], k = 1))
class(mybiplot(x = mpg[1:5], k = 1))
```

```{r}
mpg <- epa$MPG
unclass(mybiplot(x = mpg[6:10], k = 2))
class(mybiplot(x = mpg[6:10], k = 2))
```
```{r}
mpg <- epa$MPG
unclass(mybiplot(x = mpg[11:15], k = 3))
class(mybiplot(x = mpg[11:15], k = 3))
```

    
    
  2. print.math4753biplotKDeason
  
  _print.math4753biplotKDeason_ is a method for the print generic. It takes the S3 constructed from _mybiplot_ and returns a histogram of the data passed to x.
  
  _Examples:_
```{r}
mpg <- epa$MPG
print(mybiplot(x = mpg, k = 1))
```

```{r}
mpg <- epa$MPG
print(mybiplot(x = mpg, k = 2))
```

```{r}
mpg <- epa$MPG
print(mybiplot(x = mpg, k = 3))
```
      
      
  3. summary.math4753biplotKDeason
  
  _sumary.math4753biplotKDeason_ is a method for the summary generic. It takes the S3 constructed from _mybiplot_ and returns a summary of the data passed to x, grouped by the new inout variable. This summary includes [mean, median, IQR, and n].
  
  _Examples_
```{r}
mpg <- epa$MPG
summary(mybiplot(x = mpg, k = 1))
```

```{r}
mpg <- epa$MPG
summary(mybiplot(x = mpg, k = 2))
```

```{r}
mpg <- epa$MPG
summary(mybiplot(x = mpg, k = 3))
```
